Data Wrangling and Statistical Analysis of Assessment of Abundance, Aggregation, and Web Placement of *Agelenopsis pennsylvanica*

### 2022-11-23 data_analysis.Rmd
Finished analyzing the variables and fixing convergence issues; next step is to make the figures for the manuscript

global <- glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_sd_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_sd_o)
out
info <- out[[12]]
#TotalSub (log_TotalSub)
exp(info[4, 1])
exp(info[4, 2])
#Traffic_Dist_Road (log_tdr)
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Highway (log_tdh)
exp(info[2, 1])
exp(info[2, 2])

@@

# urban forest
global <- glm(WalkDist ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_sd_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_sd_f)
out
info <- out[[12]]
#tree100m
info[5, 1]
info[5, 2]
#TotalSub
-exp(info[4, 1])
exp(info[4, 2])
#Traffic_Dist_Road
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Highway
exp(info[2, 1])
exp(info[2, 2])
with(summary(top_model_sd_f), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2

# urban center
global <- glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_sd_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_sd_c)
out
info <- out[[12]]
#TotalSub
exp(info[5, 1])
exp(info[5, 2])
#patch_area_km
exp(info[2, 1])
exp(info[2, 2])
#spec_rad
info[6, 1]
info[6, 2]
#Traffic_Dist_Road
exp(info[4, 1])
exp(info[4, 2])
#Traffic_Dist_Highway
exp(info[3, 1])
exp(info[3, 2])
with(summary(top_model_sd_c), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
car::vif(get.models(model_dredge, 1)[[1]]) # road and highway disturbance between 2 and 3
```

@@

global <- glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_o)
out
info <- out[[12]]
#TotalSub (log_TotalSub)
exp(info[4, 1])
exp(info[4, 2])
#Traffic_Dist_Road (log_tdr)
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Highway (log_tdh)
exp(info[2, 1])
exp(info[2, 2])

@@

# urban forest
global <- glm(NumWebs ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_f)
out
info <- out[[12]]
with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2

# urban center
global <- glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_c)
out
info <- out[[12]]
#TotalSub
exp(info[4, 1])
exp(info[4, 2])
#patch_area_km
exp(info[2, 1])
exp(info[2, 2])
#Traffic_Dist_Highway
exp(info[3, 1])
exp(info[3, 2])
#road_length
info[5, 1]
info[5, 2]
with(summary(top_model_nw_c), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
summary(model.avg(model_dredge, subset = delta <= 2))
# We'll use the conditional average
#TotalSub
-exp(0.659231)
exp(0.186648)
#patch_area_km
-exp(0.293327)
exp(0.113716)
#Traffic_Dist_Highway
-exp(1.560993)
exp(0.192352)
#road_length_m
-0.021230 
0.004766
car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
```

@@

global <- glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_ns_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_ns_o)
out
info <- out[[12]]
#TotalSub (log_TotalSub)
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Highway (log_tdh)
exp(info[2, 1])
exp(info[2, 2])

@@

# urban forest
global <- glm(NumSpiders ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_ns_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_ns_f)
out
info <- out[[12]]
with(summary(top_model_ns_f), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2

# urban center
global <- glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_ns_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_ns_c)
out
info <- out[[12]]
#TotalSub
exp(info[4, 1])
exp(info[4, 2])
#patch_area_km
exp(info[2, 1])
exp(info[2, 2])
#Traffic_Dist_Highway
exp(info[3, 1])
exp(info[3, 2])
#road_length
info[5, 1]
info[5, 2]
with(summary(top_model_ns_c), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
```

@@

global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh, data = near, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_o)
out
info <- out[[12]]
# TotalSub
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Road
exp(info[2, 1])
exp(info[2, 1])

@@

# Urban Forest
global <- glm(round(RetreatDist, 0) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch, data = near, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_f)
out
info <- out[[12]]
#tree100m
info[6, 1]
info[6, 2]
#TotalSub
-exp(info[5, 1])
exp(info[5, 2])
#Road
exp(info[4, 1])
exp(info[4, 2])
#Highway
exp(info[3, 1])
exp(info[3, 2])

@@

# This means there is quite a bit of multicollinearity. Let's try removing the variable with the highest vif.
global2 <- update(global, .~. -tree100m)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global2, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_f)
out
info <- out[[12]]
# patch
exp(info[2, 1])
exp(info[2, 2])
# tdr
exp(info[4, 1])
exp(info[4, 2])
#tdh
exp(info[3, 1])
exp(info[3, 2])
with(summary(top_model_wd_f), 1 - deviance/null.deviance)
model.sel(model_dredge) #estimates same signs
out <- summary(model.avg(model_dredge, subset = delta <= 2))
out
info <- out[[12]]
#patch
exp(info[2, 1])
exp(info[2, 2])
#tdh
exp(info[3, 1])
exp(info[3, 2])
#tdr
exp(info[4, 1])
exp(info[4, 2])
#TotalSub
exp(info[5, 1])
exp(info[5, 2])
car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2

# Urban Center
global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = near, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_c)
out
info <- out[[12]]
#TotalSub
exp(info[5, 1])
exp(info[5, 2])
#tdr
exp(info[4, 1])
exp(info[4, 2])
#tdh
exp(info[3, 1])
exp(info[3, 2])
#log_patch
exp(info[2, 1])
exp(info[2, 2])
#spec_rad
info[7, 1]
info[7, 2]
#road_length_m
info[6, 1]
info[6, 2]

@@

global2 <- update(global, .~. -spec_rad)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global2, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_c)
out
info <- out[[12]]
car::vif(get.models(model_dredge, 1)[[1]])

@@

global3 <- update(global2, .~. -road_length_m)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global3, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_c)
out
info <- out[[12]]
# patch
exp(info[2, 1])
exp(info[2, 2])
# tdh
exp(info[3, 1])
exp(info[3, 2])
# tdr
exp(info[4, 1])
exp(info[4, 2])
with(summary(top_model_wd_c), 1 - deviance/null.deviance)
model.sel(model_dredge) #estimates same signs
out <- summary(model.avg(model_dredge, subset = delta <= 2))
out
car::vif(get.models(model_dredge, 1)[[1]]) #looks better
```

@@

myFunc <- function(mm) {
    predict(mm, newdata = predictions, re.form = ~0, type = "response")
}
#bigBoot_height_location <- bootMer(height, myFunc, nsim = 1000)
#saveRDS(bigBoot_height_location, file = "bootstrapping/bigBoot_height_location")
bigBoot_height_location <- readRDS("bootstrapping/bigBoot_height_location")
predSE <- t(apply(bigBoot_height_location$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(height, ~Location | Neighbor,type = "response"))

@@

myFunc <- function(mm) {
    predict(mm, newdata = predictions, re.form = ~0, type = "response")
}
#bigBoot_height_location2 <- bootMer(height2, myFunc, nsim = 1000)
#saveRDS(bigBoot_height_location2, file = "bootstrapping/bigBoot_height_location2")
bigBoot_height_location2 <- readRDS("bootstrapping/bigBoot_height_location2")
predSE <- t(apply(bigBoot_height_location2$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(height2, ~Location | Neighbor,type = "response"))

@@

global <- glmer(ceiling(RetreatHeight) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wh_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wh_o)
out
info <- out[[10]]
# TotalSub
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Road
exp(info[2, 1])
exp(info[2, 1])

@@

# Urban Forest
global <- glmer(ceiling(RetreatHeight) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch + (1 | ID), data = webs, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wh_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wh_f)
out
info <- out[[10]]

#TotalSub
-exp(info[3, 1])
exp(info[3, 2])
#Road
exp(info[2, 1])
exp(info[2, 2])

r.squaredGLMM(top_model_wh_f) 
model.sel(model_dredge) #estimates same signs
out <- summary(model.avg(model_dredge, subset = delta <= 2))
out
info <- out[[10]]
#tdr
exp(info[2, 1])
exp(info[2, 2])
#TotalSub
exp(info[3, 1])
exp(info[3, 2])
#tdh
exp(info[4, 1])
exp(info[4, 2])
#tree
(info[5, 1])
(info[5, 2])
#patch
exp(info[6, 1])
exp(info[6, 2])
car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2

# Urban Center
global <- glmer(ceiling(RetreatHeight) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m + (1 | ID), data = webs, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wh_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wh_c)
out
info <- out[[10]]
#TotalSub
exp(info[3, 1])
exp(info[3, 2])
#tdr
exp(info[2, 1])
exp(info[2, 2])

r.squaredGLMM(top_model_wh_c) 
model.sel(model_dredge) #estimates same signs
out <- summary(model.avg(model_dredge, subset = delta <= 2))
out
info <- out[[10]]
#tdr
exp(info[2, 1])
exp(info[2, 2])
#TotalSub
exp(info[3, 1])
exp(info[3, 2])
#tdh
exp(info[4, 1])
exp(info[4, 2])
#patch
exp(info[5, 1])
exp(info[5, 2])
#road length
exp(info[6, 1])
exp(info[6, 2])
#spec_rad
exp(info[7, 1])
exp(info[7, 2])
car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
```

*Overall* 
Fixed effects:
             Estimate Std. Error z value Pr(>|z|)    
(Intercept)    3.1824     0.6117   5.202 1.97e-07 ***
log_tdr       -0.1846     0.1007  -1.834  0.06665 .  
log_TotalSub   0.4715     0.1633   2.888  0.00388 **

R-squared = 0.3635599 (marginal - fixed) 0.9508324 (conditional - fixed and random)

>>>>

global <- glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_sd_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_sd_o)
out
info <- out[[12]]
#TotalSub (log_TotalSub)
exp(info[4, 1])
exp(info[4, 2])
#Traffic_Dist_Road (log_tdr)
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Highway (log_tdh)
exp(info[2, 1])
exp(info[2, 2])

@@

# urban forest
global <- glm(WalkDist ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_sd_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_sd_f)
out
info <- out[[12]]
#tree100m
info[5, 1]
info[5, 2]
#TotalSub
-exp(info[4, 1])
exp(info[4, 2])
#Traffic_Dist_Road
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Highway
exp(info[2, 1])
exp(info[2, 2])
with(summary(top_model_sd_f), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2

# urban center
global <- glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_sd_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_sd_c)
out
info <- out[[12]]
#TotalSub
exp(info[5, 1])
exp(info[5, 2])
#patch_area_km
exp(info[2, 1])
exp(info[2, 2])
#spec_rad
info[6, 1]
info[6, 2]
#Traffic_Dist_Road
exp(info[4, 1])
exp(info[4, 2])
#Traffic_Dist_Highway
exp(info[3, 1])
exp(info[3, 2])
with(summary(top_model_sd_c), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
car::vif(get.models(model_dredge, 1)[[1]]) # road and highway disturbance between 2 and 3
```

@@

global <- glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_o)
out
info <- out[[12]]
#TotalSub (log_TotalSub)
exp(info[4, 1])
exp(info[4, 2])
#Traffic_Dist_Road (log_tdr)
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Highway (log_tdh)
exp(info[2, 1])
exp(info[2, 2])

@@

# urban forest
global <- glm(NumWebs ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_f)
out
info <- out[[12]]
with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2

# urban center
global <- glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_nw_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_nw_c)
out
info <- out[[12]]
#TotalSub
exp(info[4, 1])
exp(info[4, 2])
#patch_area_km
exp(info[2, 1])
exp(info[2, 2])
#Traffic_Dist_Highway
exp(info[3, 1])
exp(info[3, 2])
#road_length
info[5, 1]
info[5, 2]
with(summary(top_model_nw_c), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
summary(model.avg(model_dredge, subset = delta <= 2))
# We'll use the conditional average
#TotalSub
-exp(0.659231)
exp(0.186648)
#patch_area_km
-exp(0.293327)
exp(0.113716)
#Traffic_Dist_Highway
-exp(1.560993)
exp(0.192352)
#road_length_m
-0.021230 
0.004766
car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
```

@@

global <- glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_ns_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_ns_o)
out
info <- out[[12]]
#TotalSub (log_TotalSub)
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Highway (log_tdh)
exp(info[2, 1])
exp(info[2, 2])

@@

# urban forest
global <- glm(NumSpiders ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_ns_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_ns_f)
out
info <- out[[12]]
with(summary(top_model_ns_f), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2

# urban center
global <- glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_ns_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_ns_c)
out
info <- out[[12]]
#TotalSub
exp(info[4, 1])
exp(info[4, 2])
#patch_area_km
exp(info[2, 1])
exp(info[2, 2])
#Traffic_Dist_Highway
exp(info[3, 1])
exp(info[3, 2])
#road_length
info[5, 1]
info[5, 2]
with(summary(top_model_ns_c), 1 - deviance/null.deviance) # This gives the R squared value
model.sel(model_dredge) #estimates same signs
#summary(model.avg(model_dredge, subset = delta <= 2))
car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
```

@@

global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh, data = near, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_o)
out
info <- out[[12]]
# TotalSub
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Road
exp(info[2, 1])
exp(info[2, 1])

@@

# Urban Forest
global <- glm(round(RetreatDist, 0) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch, data = near, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_f)
out
info <- out[[12]]
#tree100m
info[6, 1]
info[6, 2]
#TotalSub
-exp(info[5, 1])
exp(info[5, 2])
#Road
exp(info[4, 1])
exp(info[4, 2])
#Highway
exp(info[3, 1])
exp(info[3, 2])

@@

# This means there is quite a bit of multicollinearity. Let's try removing the variable with the highest vif.
global2 <- update(global, .~. -tree100m)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global2, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_f)
out
info <- out[[12]]
# patch
exp(info[2, 1])
exp(info[2, 2])
# tdr
exp(info[4, 1])
exp(info[4, 2])
#tdh
exp(info[3, 1])
exp(info[3, 2])
with(summary(top_model_wd_f), 1 - deviance/null.deviance)
model.sel(model_dredge) #estimates same signs
out <- summary(model.avg(model_dredge, subset = delta <= 2))
out
info <- out[[12]]
#patch
exp(info[2, 1])
exp(info[2, 2])
#tdh
exp(info[3, 1])
exp(info[3, 2])
#tdr
exp(info[4, 1])
exp(info[4, 2])
#TotalSub
exp(info[5, 1])
exp(info[5, 2])
car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2

# Urban Center
global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = near, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_c)
out
info <- out[[12]]
#TotalSub
exp(info[5, 1])
exp(info[5, 2])
#tdr
exp(info[4, 1])
exp(info[4, 2])
#tdh
exp(info[3, 1])
exp(info[3, 2])
#log_patch
exp(info[2, 1])
exp(info[2, 2])
#spec_rad
info[7, 1]
info[7, 2]
#road_length_m
info[6, 1]
info[6, 2]

@@

global2 <- update(global, .~. -spec_rad)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global2, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_c)
out
info <- out[[12]]
car::vif(get.models(model_dredge, 1)[[1]])

@@

global3 <- update(global2, .~. -road_length_m)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global3, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wd_c)
out
info <- out[[12]]
# patch
exp(info[2, 1])
exp(info[2, 2])
# tdh
exp(info[3, 1])
exp(info[3, 2])
# tdr
exp(info[4, 1])
exp(info[4, 2])
with(summary(top_model_wd_c), 1 - deviance/null.deviance)
model.sel(model_dredge) #estimates same signs
out <- summary(model.avg(model_dredge, subset = delta <= 2))
out
car::vif(get.models(model_dredge, 1)[[1]]) #looks better
```

@@

myFunc <- function(mm) {
    predict(mm, newdata = predictions, re.form = ~0, type = "response")
}
#bigBoot_height_location <- bootMer(height, myFunc, nsim = 1000)
#saveRDS(bigBoot_height_location, file = "bootstrapping/bigBoot_height_location.Rds")
bigBoot_height_location <- readRDS("bootstrapping/bigBoot_height_location.Rds")
predSE <- t(apply(bigBoot_height_location$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(height, ~Location | Neighbor,type = "response"))

@@

myFunc <- function(mm) {
    predict(mm, newdata = predictions, re.form = ~0, type = "response")
}
#bigBoot_height_location2 <- bootMer(height2, myFunc, nsim = 1000)
#saveRDS(bigBoot_height_location2, file = "bootstrapping/bigBoot_height_location2.Rds")
bigBoot_height_location2 <- readRDS("bootstrapping/bigBoot_height_location2.Rds")
predSE <- t(apply(bigBoot_height_location2$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(height2, ~Location | Neighbor,type = "response"))

@@

global <- glmer(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs, family = poisson)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wh_o <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wh_o)
out
info <- out[[10]]
# TotalSub
exp(info[3, 1])
exp(info[3, 2])
#Traffic_Dist_Road
exp(info[2, 1])
exp(info[2, 1])

@@

# Urban Forest
webs_forest <- webs_forest %>% 
  mutate(tree100m_frac = I(tree100m/100))
global <- glmer(round(RetreatHeight, 0) ~ tree100m_frac + log_TotalSub + log_tdr + log_tdh + log_patch + (1 | ID), data = webs_forest, family = poisson, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wh_f <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wh_f)
out
info <- out[[10]]

#tree
exp(info[2, 1])
exp(info[2, 2])

r.squaredGLMM(top_model_wh_f) 
model.sel(model_dredge) #estimates same signs
out <- summary(model.avg(model_dredge, subset = delta <= 2))
out
info <- out[[10]]
#tree
exp(info[2, 1])
exp(info[2, 2])
#TotalSub
exp(info[3, 1])
exp(info[3, 2])
#tdr
exp(info[4, 1])
exp(info[4, 2])

#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2

# Urban Center
global <- glmer(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + scale(spec_rad, center = FALSE) + log_patch + scale(road_length_m, center = FALSE) + (1 | ID), data = webs_center, family = poisson,  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_wh_c <- get.models(model_dredge, subset = 1)[[1]]
out <- summary(top_model_wh_c)
out
info <- out[[10]]
#TotalSub
exp(info[2, 1])
exp(info[2, 2])

r.squaredGLMM(top_model_wh_c) 
model.sel(model_dredge) #estimates same signs
out <- summary(model.avg(model_dredge, subset = delta <= 2))
out
info <- out[[10]]
#TotalSub
exp(info[2, 1])
exp(info[2, 2])
#road length
exp(info[3, 1])
exp(info[3, 2])
#tdh
exp(info[4, 1])
exp(info[4, 2])
#tdr
exp(info[5, 1])
exp(info[5, 2])
#patch
exp(info[6, 1])
exp(info[6, 2])
#spec_rad
exp(info[7, 1])
exp(info[7, 2])
#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
```

*Overall* 
Fixed effects:
             Estimate Std. Error z value Pr(>|z|)    
(Intercept)    3.1686     0.6215   5.098 3.43e-07 ***
log_tdr       -0.1896     0.1023  -1.854  0.06378 .   *negative*
log_TotalSub   0.4812     0.1659   2.901  0.00372 **  *positive*

R-squared = 0.3671774 (marginal - fixed) 0.9521663 (conditional - fixed and random)

(conditional average) 
             Estimate Std. Error Adjusted SE z value Pr(>|z|)   
(Intercept)    3.3701     1.2954      1.3012   2.590  0.00959 **
log_tdr       -0.1986     0.1022      0.1032   1.924  0.05432 .  
log_TotalSub   0.4697     0.1814      0.1830   2.567  0.01026 * 
log_tdh       -0.3307     0.2719      0.2745   1.205  0.22832
